fdcoexist

### 2018-10-04 meta_simulations.Rmd
Variation in A & k plus stronger filter
Co-authored-by: Rekyt <matthias.grenie@ens-lyon.fr>
Co-authored-by: pierredenelle <pierre.denelle@cefe.cnrs.fr>

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 8, fig.height = 10.5)

# Packages ---------------------------------------------------------------------
suppressPackageStartupMessages({
    suppressWarnings({
        library("cowplot")
        library("tidyverse")
        library("directlabels")
    })
})
# Functions --------------------------------------------------------------------
compute_moments = function(simulation_routine, trait_df = traits) {
    # CWM computation
    ab_rel = (simulation_routine$compo[,,150] /
                  rowSums(simulation_routine$compo[,,150]))
    cwm_df = ab_rel %*% trait_df
    # Values stored in moments_df
    moments_df = as.data.frame(cwm_df)
    colnames(moments_df) = "cwm"
    moments_df = tibble::rownames_to_column(moments_df, "patch")
    moments_df$env = seq(patches)
    # Add CWV
    cwv_df = (ab_rel %*% trait_df^2) - cwm_df^2
    cwv_df = as.data.frame(cwv_df)
    colnames(cwv_df) = "cwv"
    cwv_df = tibble::rownames_to_column(cwv_df, "patch")
    moments_df = dplyr::left_join(moments_df, cwv_df, by = "patch")

    return(moments_df)
}

# Compute a data.frame of number of individuals in function of optimal trait
# for competition and growth
landscape_df = function(multiple_traits_scenario, trait_df, trait_weights,
                        time = 150) {

@@

n_patches <- 25   # Number of patches
n_species <- 100  # Number of species
n_gen     <- 150  # Length of model run (generations)
initpop   <- 50   # initial population size
n_traits  <- 3    # number of traits
k         <- 1.15 # Maximum growth rate
env_width <- seq(10, 10, length.out = n_patches)  # Envtal filter strength
var_width <- seq(10, 1, length.out = n_patches) # Varying envtal filter strength
total_runs = 200  # Number of set of traits to test

@@

meta_simul = function(seed_number, given_k = k) {
    set.seed(seed_number)
    uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                       cor_coef = 0)
    set.seed(seed_number)
    low_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                         cor_coef = 0.3)

@@

    all_env = list(constant = env_width,
                   varying  = var_width)

    all_compet = list(no_compet = list(A = 0, B = B),
                      compet    = list(A = A, B = B))

@@

# Generate traits --------------------------------------------------------------
trait_seed = 5
# Make traits with different correlations
set.seed(trait_seed)
uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                   cor_coef = 0)
set.seed(trait_seed)
low_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                     cor_coef = 0.3)

@@

lab_compet_env = labeller(
    compet_status = c(compet    = "Intra + Inter competition",
                      no_compet = "Intra Only"),
    env_width     = c(constant  = "Same Filter Strength\nAlong Gradient",
                      varying   = "Increasing Filter Strength\nAlong Gradient"))

@@

```{r}
library("furrr")

@@

>>>>

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 8, fig.height = 10.5, cache = TRUE)

# Packages ---------------------------------------------------------------------
suppressPackageStartupMessages({
    suppressWarnings({
        library("cowplot")
        library("tidyverse")
        library("directlabels")
    })
})
# Functions --------------------------------------------------------------------
# Compute a data.frame of number of individuals in function of optimal trait
# for competition and growth
landscape_df = function(multiple_traits_scenario, trait_df, trait_weights,
                        time = 150) {

@@

n_patches <- 25   # Number of patches
n_species <- 100  # Number of species
n_gen     <- 150  # Length of model run (generations)
initpop   <- 50   # initial population size
n_traits  <- 3    # number of traits
k         <- 1.15 # Maximum growth rate
env_width <- rep(10, length.out = n_patches)  # Envtal filter strength
var_width <- seq(10, 1, length.out = n_patches) # Varying envtal filter strength
total_runs = 100  # Number of set of traits to test

@@

meta_simul = function(seed_number, given_k = k, given_A = A) {
    set.seed(seed_number)
    uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                       cor_coef = 0)
    set.seed(seed_number)
    low_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                         cor_coef = 0.3)

@@

    all_env = list(constant          = env_width,
                   constant_strong   = env_width/2,
                   constant_stronger = env_width/3,
                   varying           = var_width)

    all_compet = list(no_compet = list(A = 0, B = B),
                      compet    = list(A = given_A, B = B))

@@

meta_simul2 = function(seed_number, given_k = k, given_A = A) {
    set.seed(seed_number)
    uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                       cor_coef = 0)
    set.seed(seed_number)
    low_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                         cor_coef = 0.3)

    set.seed(seed_number)
    high_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                          cor_coef = 0.7)
    all_cor = list(low_cor  = low_cor_traits)

    all_env = list(constant = env_width)

    all_compet = list(compet = list(A = given_A, B = B))

    apply(all_facets, 1, function(given_row) {
        multigen(traits = all_cor[[given_row[["cor_level"]]]],
                 trait_weights = trait_scenarios[[given_row[["scenario"]]]],
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = all_compet[[given_row[["compet_status"]]]][["A"]],
                 B = all_compet[[given_row[["compet_status"]]]][["B"]],
                 d = d,
                 k = given_k,
                 width = all_env[[given_row[["env_width"]]]]) %>%
            landscape_df(all_cor[[given_row[["cor_level"]]]],
                         trait_scenarios[[given_row[["scenario"]]]],
                         time = 150) %>%
            inner_join(all_cor[[given_row[["cor_level"]]]] %>%
                           as.data.frame() %>%
                           rownames_to_column("species"),
                       by = "species") %>%
            group_by(patch) %>%
            mutate(rel_abund = N/sum(N)) %>%
            ungroup() %>%
            mutate(compet_status = given_row[["compet_status"]],
                   env_width     = given_row[["env_width"]],
                   cor_level     = given_row[["cor_level"]],
                   scenario      = given_row[["scenario"]],
                   seed_number = seed_number) %>%
            select(seed_number, compet_status, env_width, cor_level, scenario,
                   everything())
    }) %>%
        bind_rows() %>%
        filter(N != 0) %>%  # Take out absent species
        mutate_at(vars(contains("trait")), funs(cwm = rel_abund * .)) %>%
        mutate(scenario = fct_relevel(scenario, names(trait_scenarios)),
               patch_optim = as.numeric(gsub("patches", "", patch))) %>%
        group_by(seed_number, compet_status, env_width, cor_level, scenario,
                 patch) %>%
        summarise(trait1_cwm  = sum(trait1_cwm),
                  trait2_cwm  = sum(trait2_cwm),
                  trait3_cwm  = sum(trait3_cwm),
                  trait1_var  = var(trait1),
                  trait2_var  = var(trait2),
                  trait3_var  = var(trait3),
                  patch_optim = unique(patch_optim))
}
# Generate traits --------------------------------------------------------------
trait_seed = 5
# Make traits with different correlations
set.seed(trait_seed)
uncor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                   cor_coef = 0)
set.seed(trait_seed)
low_cor_traits = generate_cor_traits(n_patches, n_species, n_traits - 1,
                                     cor_coef = 0.3)

@@

lab_compet_env = labeller(
    compet_status = c(compet    = "Intra + Inter competition",
                      no_compet = "Intra Only"),
    env_width     = c(constant          = "Constant\nWide Env. Filter",
                      constant_strong   = "Constant\nStrong Env. Filter",
                      constant_stronger = "Constant\nVery Strong Env. Filter",
                      varying           = "Increasing\nFilter Strength"))

@@

```{r low_k}
library("furrr")

@@

```{r varying_A_and_k}
list_A = 2*10^-(seq(4, 6))
list_k = 1 + c(0.05, 0.15, 0.25)

plan(multiprocess(workers = availableCores() - 1))
tictoc::tic()

var_k_var_a = cross(list(run_n = seq(total_runs), A = list_A, k = list_k)) %>%
    future_map(function(x) {
    devtools::load_all()

    meta_simul2(x$run_n, x$k, x$A) %>%
        mutate(k = x$k, A = x$A)
}, .progress = TRUE)
tictoc::toc()

var_k_var_a_cwm = var_k_var_a %>%
    bind_rows() %>%
    ungroup() %>%
    nest(-k, -A, -seed_number, -scenario) %>%
    mutate(data = data %>%
               map(~.x %>%
                       gather("cwm_name", "cwm_value", ends_with("cwm")) %>%
                       group_by(cwm_name, add = TRUE) %>%
                       do(mod_cwm_env = lm(cwm_value ~ patch_optim, data = .)) %>%
                       ungroup() %>%
                       mutate(mod_glance = lapply(mod_cwm_env, broom::glance)) %>%
                       unnest(mod_glance))) %>%
    unnest(data) %>%
    filter(cwm_name == "trait2_cwm")

var_k_var_a_var = var_k_var_a %>%
    map(~.x %>%
            select(-ends_with("cwm"))) %>%
    bind_rows() %>%
    gather("var_name", "var_value", ends_with("var")) %>%
    filter(var_name == "trait2_var") %>%
    select(k, A, seed_number, everything())
```
